### 2013-04-02 drafts/grammar/grammar.tex
Added section on combining hierarchical program induction & planning.

\begin{algorithm}
\caption{Online hierarchical program induction}\label{alg:online-progind}
\begin{algorithmic}
\State Initialize $G_0$.
\For{$i\gets 1, \dots$}
\State $e_i^* = \argmax_{e} \log p(t_i|e_i) + \log p(e_i|G_{i-1}) $
\State $G_i = \argmax_{G} \log p(G|\theta) + \sum_{j \leq i} \log p(e_i|G) $
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
\caption{Online hierarchical program induction (version 1)}\label{alg:online-progind-v1}
\begin{algorithmic}
\State Initialize $G_0$.
\For{$i\gets 1, \dots$}
\State $e_i^* = \argmax_{e} \log p(t_i|e_i) + \log p(e_i|G_{i-1}) $
\State $G_i = \argmax_{G} \log p(G|\theta) + \sum_{j \leq i} \log p(e_j|G) $
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Online hierarchical program induction (version 2)}\label{alg:online-progind-v2}
\begin{algorithmic}
\State Initialize $G_0$.
\For{$i\gets 1, \dots$}
\State $F_i \sim \text{ i.i.d } p(\cdot | G)$
\State $e_i^* = \argmax_{e\in F_i} \log p(t_i|e_i) + \log p(e_i|G_{i-1}) $
\State $G_i = \argmax_{G} \log p(G|\theta) + \sum_{j \leq i} \log p(e_j|G) $
\EndFor
\end{algorithmic}
\end{algorithm}

\section{Combining planning with hierarchical program induction}
There is something clearly missing from this learning paradigm?
Actions, framed as programs acting on the environment, are not
proposed in a way that is contingent on the environment. But of course
the actions that we make are contingent on past behavior and sensory
input. A fundamental question, then, is how we can incorporate sensory
feedback and past behvarior into this learning paradigm.

One answer to this is to combine planning with hierarchical program
induction. In this view, a solution to a problem is not a single
program. It is a series of programs, each of which attempts to get the
planner closer to the goal. The goal of the learner is to a learn a
distribution over programs that takes as input a sequence of past
actions and their effects and produces a new sequence of actions.

Let's consider a concrete example of such a domain: consider the
classic AI problem of stacking blocks to build a tower of a given
height. Let's make this problem somewhat more challenging by having
the agent build this tower on a vibrating platform. We define the
domain of primitive actions to be placing a block in either horizontal
or vertical orientation anywhere in a two dimensional vertical
plane. At any point during an attempted execution, the state of the
system is the sequence of previous primitive actions, and, perhaps,
auxiliary sensory information: in this case, an agent may make use of
the current configuration of blocks (i.e. what the tower looks like)
or some summary statistic thereof. We further assume that there is
some heuristic function (e.g. height) which guides the choice of the
next state.

Let $S$ be a state space and let $h:S \rightarrow \mathbb{R}$ be a
reward function. The planner's goal is to maximize the expected change
in reward of any given action $e \in \mathcal{L}$. Of course, the
change in reward does not only depend on the current action; it also
depends on the current state. But to simplify matters we will ignore
that for now, and assume that the state dependence is subsumed in the
distribution $p(\Delta h | e)$. That is, the planner wants to find
grammar $G^*$ such that
\begin{align}
G^* &= \argmax_G \sum_e \Delta h \;p(\Delta h | e) \, p(e|G) \, p(G|\theta).
\end{align}

As a first attempt to solve this problem, we can simply splice
Algorithm~\ref{alg:online-progind-v2} with a greedy actor who always
picks the best available action at any moment. Here, however, there is
only one ``task,'' and we are maximizing over only the grammar. This
is described in Algorithm~\ref{alg:planning-progind-v1}.

\begin{algorithm}
\caption{Planning with online program induction (version
  1)}\label{alg:planning-progind-v1}
\begin{algorithmic}
\State Initialize $G_0$.
\For{$i\gets 1, \dots$}
\State $F_i \sim \text{ i.i.d } p_{e|G}(\cdot | G_i)$
\State $G_i = \argmax_{G} \log p(G|\theta) 
+ \log \sum_{e_j \in F_0 \cup \dots \cup F_i}
\prod_{e_j} \Delta h(e_j) \; p(e_j|G) $
\State $e_i^* = \argmax_{F_i}$
\EndFor
\end{algorithmic}
\end{algorithm}
